### 2020-02-15 Docs/Communications/2019/ILUS2019/Communication/ilus2019.tex
ext_phasediag

\date[5th December 2019]{International Land-Use Symposium 2019\\
3.1: Fractals and Multi-fractals\\
5th December 2019
}

@@

\cite{engelen2008validating} calibration/validation + map comparison

\cite{zhou2018gini} urban form / emissions

$\rightarrow$\textit{At the crossroad between Urban Simulation and Artificial Life, few models try to integrate and explain the link between Urban Form and Function}

$\rightarrow$\textit{Importance of parcimonious, stylized models: modeling as a tool to understand processes}

@@

Explore simple models to capture morphogenesis based on abstract representation of urban processes; test their ability to reproduce existing urban systems.

@@

{\tiny

Raimbault, J. (2018). Calibration of a density-based model of urban morphogenesis. PloS one, 13(9), e0203516.
}

@@

@@

@@

@@

\includegraphics[width=0.48\linewidth]{figures/correlations_deltavars-morpho_2015.png}
\includegraphics[width=0.48\linewidth]{figures/correlations_vars-morpho_2015.png}

@@

\sframe{Calibration method}{
 % setup, error
}

@@

\textit{Performance constraints: simulate $N$ mesoscopic morphogenesis models in parallel (macroscopic interactions are efficient as based on matrices)}

@@

$\rightarrow$ model implemented in \texttt{scala} and integrated within a broader library (including implementations of \cite{raimbault2018indirect} \cite{raimbault2018calibration}

\cite{favaro2011gibrat} \cite{cottineau2015modular})

\textit{Large number of parameters and output indicators}

@@

\textbf{Come to the satellite \textit{New Methods and Epistemologies to Explore Simulation Models} tomorrow afternoon in LHN-TR+05}

@@

@@

\includegraphics[height=0.49\textheight]{figures/mapparam_meanalpha_2015.png}
\includegraphics[height=0.49\textheight]{figures/mapparam_meanbeta_2015.png}

@@

@@

@@

$\rightarrow$ This rather simple model reproduces most of existing urban forms in Europe for both population distribution and road network : which intrinsic dimension to the urban system and its morphological aspect ?

$\rightarrow$ Ability to reproduce static correlations and a variety of dynamical lagged correlation regimes suggests that the model captures some of the processes of co-evolution

% implications for morphogenesis ?

@@

$\rightarrow$ Towards a dynamical calibration ? Need of dynamical data

@@

$\rightarrow$ Compare network generation in a ``fair'' way (correcting for additional parameters, open question for models of simulation)

@@

@@

@@

$\rightarrow$ Work in progress: calibration of the reaction-diffusion model on world urban areas with the Global Human Settlements Layer database

$\rightarrow$ Link with sustainability indicators: GHG emissions, economics, etc. \cite{raimbault2019multi}

@@

$\rightarrow$ A novel model of urban morphogenesis at the mesoscopic scale systematically explored: \textbf{need for more coupling and comparison of models.}

@@

\bigskip
\bigskip
\bigskip

\footnotesize{ - Code, data and results available at\\ \texttt{https://github.com/JusteRaimbault/CityNetwork}\\
- Acknowledgments: Thanks to the \textit{European Grid Infrastructure} and its \textit{National Grid Initiatives} (\textit{France-Grilles} in particular) to give the technical support and the infrastructure.

>>>>

\date[5th December 2019]{International Land-Use Symposium 2019\\
Session Drivers, Mechanisms, Tools\\
5th December 2019
}

@@

$\rightarrow$ Cellular automata models or models of land-use change generally highly data-driven

$\rightarrow$ May be case-specific or conclusions difficult to generalize (see Sleuth for example \cite{clarke2007decade})

$\rightarrow$ Issues to calibrate and validate these models \cite{engelen2008validating}

%calibration/validation + map comparison

%\cite{zhou2018gini} urban form / emissions

\textbf{Urban morphogenesis models approach:}

\smallskip

$\rightarrow$\textit{At the crossroad between Urban Simulation and Artificial Life, stylized models of urban growth processes}

$\rightarrow$\textit{Importance of parsimony: generative modeling as a tool to understand processes}

@@

$\rightarrow$ Explore a simple model to capture morphogenesis based on abstract representation of urban processes; test their ability to reproduce existing urban systems.

$\rightarrow$ The simple reaction-diffusion model of urban growth is calibrated worldwide using GHSL, and in time.

$\rightarrow$ Globally comparable insights into processes of concentration and dispersion.

@@

\textit{Raimbault, J. (2018). Calibration of a density-based model of urban morphogenesis. PloS one, 13(9), e0203516.}

@@

\begin{center}

@@

\end{center}

@@

\sframe{Correlations with urban area properties}{

@@

\includegraphics[trim={4cm 0 0 0},width=0.48\linewidth]{figures/correlations_deltavars-morpho_2015.png}
\includegraphics[trim={4cm 0 0 0},width=0.48\linewidth]{figures/correlations_vars-morpho_2015.png}

@@

\sframe{Calibration method}{
 % setup, error

\begin{itemize}
	\item For a time period $\left[t_0,t_f\right]$, model initialized with population at $t_0$
	\item Growth rate $N_G$ is computed by constraining with actual population growth: $N_G \textrm{ = } \left(P_i\left(t_f\right) - P_i \left(t_0\right)\right) / T$ where $T$ is a calibration parameter
	\item Fitness functions: squared relative population error and squared relative morphological indicator error
	\item Biobjective genetic algorithm (NSGA2) run for each areas ($\sim 600$ areas large enough) and each time windows (1000 generations, population of 100), on parameters $\alpha, \beta, T$
\end{itemize}

@@

\textit{Performance constraints: large number of calibration algorithms to be run}

@@

$\rightarrow$ model implemented in \texttt{scala} and integrated within the \texttt{spatialdata} library for spatial sensitivity analysis (including implementations of

\cite{raimbault2018indirect} \cite{raimbault2018calibration} \cite{favaro2011gibrat} \cite{cottineau2015modular})

See \url{https://github.com/openmole/spatialdata}

@@

%\textbf{Come to the satellite \textit{New Methods and Epistemologies to Explore Simulation Models} tomorrow afternoon in LHN-TR+05}

\textbf{Apply for the OpenMOLE summer school before January 15th}

\url{https://exmodelo.org/}

@@

\end{center}

\textit{Different performance on indicator fit and forms of Pareto fronts}

@@

\includegraphics[height=0.43\textheight]{figures/mapparam_meanalpha_2015.png}

\includegraphics[height=0.43\textheight]{figures/mapparam_meanbeta_2015.png}

@@

\begin{center}

\includegraphics[height=0.49\textheight]{figures/phasediag_largestcities_moran_tsteps50.png}
\includegraphics[height=0.49\textheight]{figures/phasediag_largestcities_slope_tsteps50.png}

\end{center}

\textit{Urban areas trajectories can be projected into model phase diagrams}

@@

\end{center}

\textit{Slight significant correlations with growth rates of GHG emissions: more aggregation correlates with decreasing emissions e.g.}

@@

\smallskip

$\rightarrow$ This rather simple model can effectively be calibrated on worldwide urban areas and provide comparable growth parameters

$\rightarrow$ Link between urban form, urban dynamics and sustainability properties

@@

\smallskip

$\rightarrow$ Benchmark with other simple models (e.g. \cite{li2019singularity} presented yesterday)

$\rightarrow$ Coupling with macro-scale model for system of cities \cite{raimbault:halshs-02351722}

@@

%$\rightarrow$ Compare network generation in a ``fair'' way (correcting for additional parameters, open question for models of simulation)

@@

Within the same stream of modeling (complementary to more classical approaches to land-use change):

@@

\smallskip

@@

\smallskip

$\rightarrow$ More systematic link with sustainability indicators: GHG emissions, economics, etc. \cite{raimbault2019multi}

@@

$\rightarrow$ A simple model of urban morphogenesis at the mesoscopic scale systematically calibrated: \textbf{need for more benchmarking and comparison of models.}

\smallskip

@@

\textbf{Use and contribute to OpenMOLE: } \url{https://github.com/openmole}

\textbf{Apply to the summer school: } \url{https://exmodelo.org/}

\footnotesize{ - Code, data and results available at \texttt{https://github.com/JusteRaimbault/UrbanGrowth}\\
- Acknowledgments: Thanks to the \textit{European Grid Infrastructure} and its \textit{National Grid Initiatives} (\textit{France-Grilles} in particular) to give the technical support and the infrastructure.

### 2020-02-15 Docs/Communications/ignored/XTerM2019/extendedAbstract.tex

>>>>

We propose the following specification for the strong coupling. At a time step of the macro level $\Delta t_{\mu}$:
\begin{itemize}
	\item Macro level interaction model is computed and population variations $\Delta P_i$ are obtained
	\item Meso level sprawl is simulated in the interval for each area, given this increase. Parameters are fixed by a baseline value but modified as a function of $\Delta P_i$ following simple rules % TODO
	\item The resulting urban form is used to compute an endogenous activity (still with very simple stylized rules) which modifies the macro parameters for each area (these depend then on $i$: $d_G^{(i)},g_0^{(i)}$
\end{itemize}
